outlier_exploration

### 2025-04-26 EDA/multicollinearity_and_outlier.qmd
Ethan: Removing potential outliers, R^2 value increased significantly

```{r}
full_model <- lm(sleep_duration ~., sleep)
```

@@

>>>>

```{r}
full_model <- lm(sleep_duration ~., sleep)
summary(full_model)
```

@@

# Remove the suspicious rows
sleep_clean <- sleep[-suspicious_indices, ]

# Refit the model excluding suspicious rows 
full_model_clean <- lm(sleep_duration ~ ., data = sleep_clean)

# Plot diagnostics again on the cleaned model
par(mfrow = c(2, 2))
plot(full_model_clean)

# Comparison of model summaries
summary(full_model)        # Old model (with potential outliers)  R^2  = 0.9592
summary(full_model_clean)  # New model (without potential outliers)  R^2  = 0.9929
